Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-07 paper_jasa.tex
changes along the discussion with Mahbub

\begin{tabular}{lp{5.5in}}
$W$  & is a design matrix of covariates corresponding to specifics of lineup $\ell$ and subject $i$. Covariates could include  demographic information of individuals, such as age, gender, education level etc. as well lineup-specific elements, e.g. difficulty level. \\
$\delta$ & is a vector of parameters for fixed effects.\\
$Z_{\ell i}$ & $1 \le i \le K$, $1 \le \ell \le L$  is a design matrix corresponding to random effects specific to individual $i$ and lineup $\ell$.  \\
$\tau$ & is a vector of independent real-valued random variables $\tau_{\ell i}$,  $\tau  \sim  MVN(0,\sigma_\tau I_{KL \times KL})$. $\tau$ will usually include a component incorporating an individual's ability or skill to evaluate lineups.\\
\end{tabular}
}

>>>>

\begin{tabular}{lp{5.5in}}
$W$  & is a design matrix of covariates corresponding to specifics of lineup $\ell$ and subject $i$. Covariates could include  demographic information of individuals, such as age, gender, education level etc. as well lineup-specific elements, e.g. difficulty level. \\
$\delta$ & is a vector of parameters for fixed effects.\\
$Z_{\ell i}$ & $1 \le i \le K$, $1 \le \ell \le L$  is a design matrix corresponding to random effects specific to individual $i$ and lineup $\ell$.  \\
$\tau$ & is a vector of independent real-valued random variables $\tau_{\ell i}$,  $\tau  \sim  MVN(0,\sigma_\tau I_{KL \times KL})$. $\tau$ will usually include a component incorporating an individual's ability or skill to evaluate lineups. 
Note that $t_{\ell i }$ usually only includes a partial interaction; for a full interaction of subjects' skills and lineup-specific difficulty we would need replicates of the same subject evaluating the same lineup, which in practice is not feasible without loosing independence.\\
\end{tabular}
}
